Upwelling variability across the Benguela upwelling systems

### 2019-10-08 SST_patterns.Rmd
update

```{r}
anova_func <- function(df){
  sites_aov <- aov(intensity_mean ~ site * duration * distance, data = df)
return(sites_aov)
}

@@

Create visualisation which compares the presence and absence of events
If a event is found in a particular site at a particulate dat, is the same event present in the other datasets? Show how the events detected varies between site and dataset.

```{r}
# To determine wether or not the same upwlling patterns are present at different distances from the coastline

>>>>

```{r}
options(scipen = 999)
anova_func <- function(df){
  sites_aov <- aov(intensity_mean ~ site * duration * distance, data = df)
return(sites_aov)
}

@@

Plot showing upwelling at the different sites for each of the different distances

scatter_func <- function(df){
  CMC_filtered <- df %>%
filter(year(date_start) %in% seq(2010, 2016, 1))
}

CMC_filtered <- scatter_func(df = CMC_upwell_base)
OISST_filtered <- scatter_func(df = OISST_upwell_base)
SACTN_filtered <- scatter_func(df = SACTN_upwell_base)

plot_scat_func <- function(df){
  ggplot(data = df, aes(x = date_start, y = intensity_mean)) +
  geom_point() +
  scale_x_date(expand = c(0, 0)) +
  facet_wrap(~distance, ncol = 2) +
  theme_grey() +
  labs(y = "Mean Intensity", x = NULL)
}
(CMC_plot <- plot_scat_func(df = CMC_filtered))
(OISST_plot <- plot_scat_func(df = OISST_filtered))

plot_scat_func <- function(df){
  ggplot(data = df, aes(x = date_start, y = intensity_mean)) +
  geom_point() +
  scale_x_date(expand = c(0, 0)) +
  facet_wrap(~site, ncol = 2) +
  theme_grey() +
  labs(y = "Mean Intensity", x = NULL)
}
(SACTN_plot <- plot_scat_func(df = SACTN_filtered))
```

### 2019-10-08 Write_up/Paper1_writeup.Rmd
update

<!-- \def\tiny{\@setfontsize\tiny{10pt}{11pt}} -->
\begin{tiny}
\begin{center}
\setlength\tabcolsep{3pt}
\begin{longtable}{|r|r|p{2cm}|}
\caption{OISST} \\

% This is the header for the first page of the table...
\toprule
Site & distance & slope  \\
\midrule
\endfirsthead

@@

<!-- \def\tiny{\@setfontsize\tiny{10pt}{11pt}} -->
\begin{tiny}
\begin{center}
\setlength\tabcolsep{3pt}
\begin{longtable}{|r|r|p{2cm}|}
\caption{CMC} \\

% This is the header for the first page of the table...
\toprule
Site & distance & slope  \\
\midrule
\endfirsthead

@@

<!-- \def\tiny{\@setfontsize\tiny{10pt}{11pt}} -->
\begin{tiny}
\begin{center}
\setlength\tabcolsep{3pt}
\begin{longtable}{|r|r|p{2cm}|}
\caption{SACTN} \\

% This is the header for the first page of the table...
\toprule
Site & distance & slope  \\
\midrule
\endfirsthead

@@

@@

# Plotting images

####TO do
- Plots

# Discussion

>>>>

##

<!-- \def\tiny{\@setfontsize\tiny{10pt}{11pt}} -->
\begin{tiny}
\begin{center}
\setlength\tabcolsep{3pt}
\begin{longtable}{|r|r|p{2cm}|}
\caption{The absolute cumulative intensity (°C.day) for the sites located within the Benguela upwelling system using the OISST dataset. The site column gives the name of the site. The distance column gives the distance from the coastline as seen in Fig 1. The cumulative intensity expects as absolute magnitudes rather than relative seasonal climatology} \\

% This is the header for the first page of the table...
\toprule
Site & distance & regression slope  \\
\midrule
\endfirsthead

% This is the header for the second page of the table...
\toprule
Site & distance & regression slope  \\
\midrule
\endhead

@@

<!-- \def\tiny{\@setfontsize\tiny{10pt}{11pt}} -->
\begin{tiny}
\begin{center}
\setlength\tabcolsep{3pt}
\begin{longtable}{|r|r|p{2cm}|}
\caption{The absolute cumulative intensity (°C.day) for the sites located within the Benguela upwelling system using the CMC dataset. The site column gives the name of the site. The distance column gives the distance from the coastline as seen in Fig 1. The cumulative intensity expects as absolute magnitudes rather than relative seasonal climatology} \\

% This is the header for the first page of the table...
\toprule
Site & distance & regression slope  \\
\midrule
\endfirsthead

% This is the header for the second page of the table...
\toprule
Site & distance & regression slope  \\
\midrule
\endhead

@@

<!-- \def\tiny{\@setfontsize\tiny{10pt}{11pt}} -->
\begin{tiny}
\begin{center}
\setlength\tabcolsep{3pt}
\begin{longtable}{|r|r|p{2cm}|}
\caption{The absolute cumulative intensity (°C.day) for the sites located within the Benguela upwelling system using the SACTN dataset. The site column gives the name of the site. Tempertures were collected at the coastline and not at different distances from the coastline. The cumulative intensity expects as absolute magnitudes rather than relative seasonal climatology} \\

% This is the header for the first page of the table...
\toprule
Site & distance & regression slope  \\
\midrule
\endfirsthead

@@

The linear regression analysis showed that the absolute cumulative intensity among all variables within each dataset showed the most variation. The cumulative intensity acts as absolute magnitude rather than relative seasonal climatology. When looking at the results for the data obtained from the OISST dataset it is evident that R^2 values are highest at greater distances from the coastline for each of the sites except for Port Nolloth. For examples, Lamberts Bay had an R^2 value of 5.47  at a distance of 10000km but only an R^2 value of -8.76 at 50000km. Similar trends were apparent for Saldanha Bay (R^2 -3.28 at 10000 km and -12.42 at 50000 km) and Sea Point (R^2  = -8.77 at 10000 km)

The CMC remotely sensed sea surface temperature dataset had higher R^2 values compared to the OISST dataset. Most of the sites within CMC dataset had greater R^2 values at distances furthest from the coastline. Here, Lamberts Bay had R^2 value of -26.30 for 10000km and -31.77 for 50000km respectively. Similarly, Port Nolloth had R^2 values of -15.34 at 10000km and -20.45 at 50000km. Saldanha Bay however presented its lowest value of -24.84 at 10000km and highest R^2 value of -46.39 at 40000km and also the highest value among all of the sites. Additionally, Sea Point displayed similar patterns with the lowest value occurring at a distance of 10000km from the coastline and its highest R^2 value of -38.35 occurring at a distance of 40000km from the coastline.

Lastly, the SACTN in situ collected SST data collected directly at the coastline had variable R^2 values. Lamberts Bay had an R^2 value of -1.46. Port Nolloth, representing the second highest value of -3.65. Saldanha Bay representing an R^2 value of -2.56 and the highest R^2 value of -10.96 occurring at Sea Point.

@@

## Discussion
